From Reversible Programs to \\ Univalent Universes and Back

### 2021-10-30 Pi/paper/applications.tex
Many more edits

Using our semantics, we can normalise, synthesise, prove equivalence, and reason about~$\PiLang$ programs. We describe a
few applications in this section, and a more comprehensive list of applications and examples along with their
foramlisation is available in our artifact~\cite{choudhuryArtifactSymmetriesReversible2021}.

@@

\begin{definition}[Normalisation of $\PiLang$ programs]
  \begin{gather*}
    \begin{aligned}
      \normt_{0} & : U \to \UPlus                                            \\
      \normt_{0} & = \quotep_{0} \comp \quoteh_{0} \comp \gdenot{\blank}_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \normt_{1} & : (c : X \iso Y) \to \normt_{0}(X) \iso \normt_{0}(Y)     \\
      \normt_{1} & = \quotep_{1} \comp \quoteh_{1} \comp \gdenot{\blank}_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

@@

After applying $\normt_{1}$ to each circuit, we verify that they both reduce to the same normal form
\Afun{reversibleOrNorm}, along with a 2-combinator witnessing their equivalence with the normal form -- by composing
these, we get the 2-combinator witnessing their equivalence. More general, user-guided, reasoning can be done using the
sound and complete level-2 combinators to rewrite $\PiLang$ programs.

@@

Instead of manually producing $\PiLang$-programs to implement the reversible disjunction specification, it is possible
to simply write down the permutation directly and then quote it, synthesising a $\PiLang$ program. We use a function
$\term{lookup}$ to write tabulated permutations for readability.

@@

\noindent
The permutation uses the canonical encoding of sequences of bits as natural numbers, e.g., {(\textsf{false},
    \textsf{true},\textsf{true})} is encoded as 011 or 3. The second entry in the $\term{lookup}$ table maps index 1 (= 001)
to the value 5 (= 101), following the reversible disjunction specification (recall that
$\mathsf{reversibleOr}(h,b_1,b_2) = (h \,\underline{\vee}\, (b_1 \vee b_2), ~b_1, ~b_2)$ where~$\vee$ is disjunction
and~$\underline{\vee}$ is exclusive-disjunction). Quoting this permutation generates the same normalised program
\Afun{reversibleOrNorm}, matching the desired structured type of a 1-combinator on $\mathbb{8}+$.

In a similar way we can also verify whether a circuit is correctly implemented: by running the equivalence described
above in the other direction, we can evaluate the circuit to a bijection and compare it extensionally with the intended
one.

@@

In our development, we described a number of different representations of permutations: $\PiLang$, $\PiPlusLang$ and
$\PiHatLang$ programs, lists of transpositions, Lehmer codes, and automorphisms of finite sets. The equivalences between
these representations allows us to transfer theorems about permutations, proving them on the representations most suited
for the particular task and getting others for free.

As an example, consider the following problem. Toffoli gate on 3 bits can be extended to 4 bits, inserting a wire in
four possible positions. The function of such gate is then identity on the newly inserted bit, and controlled-controlled
not on the three remaining ones.
\medskip
\extendedToffoli{}

\noindent
On the other hand, it is possible to construct a proper 4-bit toffoli gate:
\medskip
\toffoli{}

\noindent
Now, the question we want to answer is: is it possible to implement \Afun{toffoli₄} gate only using \Afun{toffoli₃} gates?

Solving this problem using the circuit representation is difficult. However, we can observe that all \Afun{toffoli₃}
gates implements even permutations, that is, permutations consisting of an even number of transpositions. On the other
hand, \Afun{toffoli₄} implements an odd permutation. It is an easily proven lemma that any composition of even
permutations always produces an even permutation, which answers the question to the negative. Thus, we want to formulate
the theorem using the representation on lists of transpositions, and transfer it to circuits using the equivalences
proven in the previous sections.

Thus, define a function $\parity : (c : X \iso Y) \to \Bool$ to compute a parity of a permutation defined by a
combinator $c$, by first tranforming a $\PiLang$ program into a list of transpositions (using $\evalh_{1}$ defined
in~\cref{sec:equivalence}), and then computing the parity on this representation, which amounts to a simple check of the
partiy of the length of the list.

\begin{propositionrep}
  \label{prop:parity-preserved}
  For two $\PiLang$ circuits $c_1, c_2$, if $c_1 \Iso c_2$, then $\parity(c_1) = \term{parity}(c_2)$.
\end{propositionrep}
\begin{proof}
  First, it is an easy check that Coxeter relations preserve parity of the list. Second, if $c_1$ and $c_2$ are related
  by a 2-combinator, then their Lehmer codes are the same, so their list-of-transpositions representations have to be
  related by the Coxeter relation. Composing these two facts completes the proof.
\end{proof}

Using ~\cref{prop:parity-preserved} and already mentioned lemma that any compostion of even circuits is even, we can
finish the proof by running $\parity$ on \Afun{toffoli₄} and on all of the \Afun{toffoli₃}.

>>>>

Using our semantics, we can normalise, synthesise, prove equivalence, and reason about~$\PiLang$ programs. We describe a
few applications in this section, and a more comprehensive list of applications and examples along with their
formalisation is available in our artifact~\cite{choudhuryArtifactSymmetriesReversible2021}.

@@

\begin{definition}[Normalisation of $\PiLang$ programs]
  \begin{gather*}
    \begin{aligned}
      \normt_{0} & : U \to \UPlus                                            \\
      \normt_{0} & = \quotep_{0} \comp \quoteh_{0} \comp \gdenot{\blank}_{0}
    \end{aligned}
    \qquad
    \begin{aligned}
      \normt_{1} & : (c : X \iso Y) \to \normt_{0}(X) \isop \normt_{0}(Y)    \\
      \normt_{1} & = \quotep_{1} \comp \quoteh_{1} \comp \gdenot{\blank}_{1}
    \end{aligned}
  \end{gather*}
\end{definition}

@@

After applying $\normt_{1}$ to each circuit, we can verify that they both reduce to the same normal form
\Afun{reversibleOrNorm}, and there exist 2-combinators between each of them and the normal form. More general,
user-guided, reasoning can be done using the sound and complete level-2 combinators to rewrite $\PiLang$ programs.
% as an example, we can manually produce a proof of equivalence of ?? and ?? -- a 2-combinator presented below: 
% \medskip
% \manualTwoCombinator{}

@@

Instead of manually writing $\PiLang$ programs to implement the reversible disjunction specification, it is possible to
simply write down the permutation directly and then quote it, synthesising a $\PiLang$ program. We show this below,
using a function $\term{lookup}$ to write tabulated permutations for readability.

@@

\noindent
The permutation uses the canonical encoding of sequences of bits as natural numbers, e.g.,
${(\mathsf{false},\mathsf{true},\mathsf{true})}$ is encoded as 011 or 3. The second entry in the $\term{lookup}$ table
maps index 1 (= 001) to the value 5 (= 101), following the reversible disjunction specification (recall that
$\mathsf{reversibleOr}(h,b_1,b_2) = (h \,\underline{\vee}\, (b_1 \vee b_2), ~b_1, ~b_2)$ where~$\vee$ is disjunction
and~$\underline{\vee}$ is exclusive-disjunction). Quoting this permutation generates the same normalised program
\Afun{reversibleOrNorm}, matching the desired structured type of a 1-combinator on $\mathbb{8}+$.

Similarly, we can also verify whether a circuit is correctly implemented -- by running the equivalence described above
in the other direction, we can evaluate the circuit to a bijection and compare it extensionally with the intended one.

@@

In our development, we described a number of different representations of permutations: $\PiLang$, $\PiPlusLang$ and
$\PiHatLang$ programs, lists of transpositions, Lehmer codes, and automorphisms of finite sets. The equivalences between
these representations allow us to transfer theorems about permutations -- we prove them on the most suitable
representation, and then transport them to a different representation ``for free''.

As an example, consider the following problem. The Toffoli gate on 3 bits can be extended to a reversible gate on 4
bits, by inserting a wire in four possible positions. This gate performs identity on the newly inserted bit, and
controlled-controlled not on the three remaining ones. We show how to write these gates using \Afun{cif}.
\medskip
\extendedToffoli{}

\noindent
On the other hand, it is possible to construct a proper 4-bit toffoli gate.
\medskip
\toffoli{}

\noindent
Now, we can ask: is it possible to implement \Afun{toffoli₄} gate using only \Afun{toffoli₃} gates?
\medskip

Solving this problem in the circuit representation is difficult. However, we can observe that all \Afun{toffoli₃} gates
implement even permutations, that is, permutations that perform an even number of transpositions. On the other hand,
\Afun{toffoli₄} implements an odd permutation. It can be easily proved that any composition of even permutations always
produces an even permutation, which answers the question to the negative. Thus, we formulate the theorem using the
representation of lists of transpositions, and transfer it to circuits using the equivalences proven in the previous
sections.

We define a function $\parity : (X \iso Y) \to \Bool$ to compute the parity of a permutation defined by a combinator
$c$, by first transforming a $\PiLang$ program into a list of transpositions (using $\evalh_{1}$ defined
in~\cref{sec:equivalence}), and then computing the parity of this representation, which amounts to a simple checking of
the parity of the length of the list.

\begin{propositionrep}
  \label{prop:parity-preserved}
  For two $\PiLang$ circuits $c_1, c_2$, if $c_1 \Iso c_2$, then $\parity(c_1) = \term{parity}(c_2)$.
\end{propositionrep}
\begin{proof}
  First, it is easy to check that Coxeter relations preserve parity of the list. Second, if $c_1$ and $c_2$ are related
  by a 2-combinator, then their Lehmer codes are the same, so their list-of-transpositions representations have to be
  related by the Coxeter relation. Composing these two facts completes the proof.
\end{proof}

\noindent
Using~\cref{prop:parity-preserved} and the fact that any composition of even circuits is even, we complete the proof by
computing the $\parity$ of \Afun{toffoli₄}, and all of the \Afun{toffoli₃} combinations.

### 2021-10-30 Pi/paper/equivalence.tex
Many more edits

To produce a braiding $n + m \isoh m + n$ from adjacent tranpositions, we recursively traverse the left subexpression,
swapping each element using adjacent transpositions along the elements on the right, placing it in the right position.
The computational content of this translation can be visualised using tree transformations, for the recursive case
in~\cref{fig:plusplusswap}. The challenging part is showing that these moves are coherent with respect to 2-combinators.

>>>>

To produce a braiding $n + m \isoh m + n$ from adjacent transpositions, we recursively traverse the left subexpression,
swapping each element using adjacent transpositions along the elements on the right, placing it in the right position.
The computational content of this translation can be visualised using tree transformations, for the recursive case
in~\cref{fig:plusplusswap}. The challenging part is showing that these moves are coherent with respect to 2-combinators.

### 2021-10-30 Pi/paper/finite.tex
Many more edits

Bubble sort uses the primitive operation of adjacent swaps, insertion sort and selection sort use the primitive
operation of swapping the $i$-th element with the $j$-th element, cycle sort uses cyclical shifts of subsequences,
pancake sort uses reversals of the prefixes of the list, et cetera. The choice of generators for our presentation is
important for the following reasons.

@@

We will show that it is possible to encode all $\PiLang$ combinators using adjacent transpositions
(in~\cref{sec:equivalence}).
%Group presentations are built by adding equations to a \emph{free group}.

@@

Usually, there are are many equations, besides the group axioms, that hold for the elements of a group. For example, in
the group $\Aut[\Bool]$, or $\mathbb{Z}_2$, we have an equation $1 + 1 = 0$, which is not a consequence of the group
axioms, but is specific to this particular group. A free group has the property that no other equations hold except the
ones directly implied by the group axioms. For example, the additive group of integers $\mathbb{Z}$ is the free group on
the singleton set.

@@

Instead, we will think about elements of the free group as words over an alphabet of letters drawn from the generating
set \emph{and} the set of their formal inverses. If we take the disjoint union of $A$ with itself, that is, $A + A$ as
the group's underlying set, we can use $\inl/\inr$ to mark the elements -- $\inl{a}$ means $a$ and $\inr{a}$ means
$\inv{a}$. Then, we can encode the free group using the free monoid, that is, lists of $A + A$. Additionally, we need to
ensure that the inverse laws hold, so we have to coalesce adjacent occurences of $a$ and $\inv{a}$.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}

@@

For this to work, we first need the system to have the termination property, meaning that there should be no infinite
reductions. We observe that after throwing out reflexivity and symmetry, the right hand sides of the relations $\cox*$
are strictly smaller than the left hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$ (which is
well-founded). Thus, by directing the relation from left to right, we would get the termination property out of the box.
Second, we need the normal forms to be unique, so that we can extract a normalisation function. This will be true if the
rewriting system is confluent -- all critical pairs, that is, terms with overlapping possible reduction rules, have to
converge. For example, in our system, the pair in~\cref{fig:critical-pairs-converging} converges. Unfortunately, this is
not true for all critical pairs -- an example is in~\cref{fig:critical-pairs-non-converging}, where left and right
endpoints are normal with respect to the $\cox*$ relation.

@@

\noindent The result of computing $n \downf k$ is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\), which
is a sequence of transpositions that moves the element at index $k + n$ left by $k$ places, shifting all the elements in
between one place right (see~\cref{fig:downf}). Then, the directed relation $\longcox$ is defined with the following
generators (inlining the congruence closure in $\longcox$ allows arbitrary reductions inside the list).

@@

Note that the previous $\braid$ rule is a special case of $\longbraid$, with $k = 0$. As before, the left-hand sides of
the relation are (lexicographically) strictly larger than the right-hand sides. We define the transitive closure of
$\longcox$ to be $\longcoxplus$ (\cref{def:longcox-plus}) and its reflexive-transitive closure to be $\longcoxstar$
(\cref{def:longcox-star}).

@@

The modified form of the Coxeter relations are unwieldy and difficult to prove properties about by induction. However,
we can make the following observation relating it to $\cox*$.

@@

By~\cref{prop:nf}~\ref{prop:nf-uniqueness}, we get a unique choice function $\normf : {\List[\Fin[n]]} \to
  {\List[\Fin[n]]}$ that produces a normal form for terms of $\List[\Fin[n]]$. We state two important properties enjoyed
by $\normf$.

@@

\noindent
Notice however, that for a group presentation, as defined in~\cref{def:presentation}, the relation needs to be on the
set of words $A + A$, where the right copy corresponds to the set of formal inverses of the generators. The following
proposition lets us lift a group structure on $\List[A]$ to a group presentation.

@@

\begin{proof}
  Let $G$ be the group on $\List[A]$. We construct the group homomorphism from $F(\langle A ; \liftrel{R} \rangle)$ to
  $G$ using the universal property of the group presentation, where the map on generators is given by taking the
  singleton list. To construct the group homomorphism from $G$, we use the universal property of the set quotient, where
  the map on the underlying set is given by mapping $\inl$ on the list. Using that the relation is a congruence, we show
  that this consttitutes a group isomorphism.
\end{proof}

@@

The inversion count of an element is the number of smaller elements appearing after it in the permutation.

@@

\noindent We can show that the function $\immersion_{n}$ gives an equivalence betweeen $\Lehmer[n]$ and $\im{\normf}$.

>>>>

\noindent
Bubble sort uses the primitive operation of adjacent swaps, insertion sort and selection sort use the primitive
operation of swapping the $i$-th element with the $j$-th element, cycle sort uses cyclical shifts of subsequences,
pancake sort uses reversals of the prefixes of the list, et cetera. The choice of generators for our presentation is
important for the following reasons.

@@

\noindent
We will show in~\cref{sec:equivalence} that all $\PiLang$ combinators can be encoded using adjacent transpositions.
%Group presentations are built by adding equations to a \emph{free group}.

@@

Usually, there are many equations, besides the group axioms, that hold for the elements of a group. For example, in
the group $\Aut[\Bool]$, or $\mathbb{Z}_2$, we have an equation $1 + 1 = 0$, which is not a consequence of the group
axioms, but is specific to this particular group. A free group has the property that no other equations hold except the
ones directly implied by the group axioms. For example, the additive group of integers $\mathbb{Z}$ is the free group on
the singleton set.

@@

Instead, we will think about elements of the free group as words over an alphabet of letters drawn from the generating
set \emph{and} the set of their formal inverses. If we take the disjoint union of $A$ with itself, that is, $A + A$ as
the group's underlying set, we can use $\inl/\inr$ to mark the elements -- $\inl{a}$ means $a$ and $\inr{a}$ means
$\inv{a}$. Then, we can encode the free group using the free monoid, that is, lists of $A + A$. Additionally, we need to
ensure that the inverse laws hold, so we have to coalesce adjacent occurrences of $a$ and $\inv{a}$.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(=\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diagrams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}

@@

For this to work, we first need the system to have the termination property, meaning that there should be no infinite
reductions. We observe that after throwing out reflexivity and symmetry, the right-hand sides of the relations $\cox*$
are strictly smaller than the left-hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$ (which is
well-founded). Thus, by directing the relation from left to right, we would get the termination property out of the box.
Second, we need the normal forms to be unique, so that we can extract a normalisation function. This will be true if the
rewriting system is confluent -- all critical pairs, that is, terms with overlapping possible reduction rules, have to
converge. For example, in our system, the pair in~\cref{fig:critical-pairs-converging} converges. Unfortunately, this is
not true for all critical pairs -- an example is in~\cref{fig:critical-pairs-non-converging}, where left and right
endpoints are normal with respect to the $\cox*$ relation.

@@

\noindent The result of computing $n \downf k$ is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\), which
is a sequence of transpositions that moves the element at index $k + n$ left by $k$ places, shifting all the elements in
between one place right (see~\cref{fig:downf}). Then, the directed relation $\longcox$ is defined with the following
generators (inlining the congruence closure in the relation $\longcox$ allows arbitrary reductions inside the list).

@@

Note that the previous $\braid$ rule is a special case of $\longbraid$, with $k = 0$. As before, the left-hand sides of
the relation are (lexicographically) strictly larger than the right-hand sides. We define the transitive closure of
$\longcox$ to be $\longcoxplus$ (see~\cref{def:longcox-plus} in the appendix) and its reflexive-transitive closure to be
$\longcoxstar$ (see~\cref{def:longcox-star}).

@@

\noindent
The modified form of the Coxeter relations are unwieldy and difficult to prove properties about by induction. However,
we can make the following observation relating it to $\cox*$.

@@

\noindent
By~\cref{prop:nf}~part~\ref{prop:nf-uniqueness}, we get a unique choice function $\normf : {\List[\Fin[n]]} \to
{\List[\Fin[n]]}$ that produces a normal form for terms of $\List[\Fin[n]]$. We state two important properties enjoyed
by $\normf$.

@@

\noindent
Notice however, that for a group presentation, as defined in~\cref{def:presentation}, the relation needs to be on the
set of words $A + A$, where the right copy corresponds to the set of formal inverses of the generators. The following
proposition lets us lift a group structure on $\List[A]$ to a group presentation, with underlying set $\List[A+A]$.

@@

\begin{proof}
  Let $G$ be the group on $\List[A]$. We construct the group homomorphism from $F(\langle A ; \liftrel{R} \rangle)$ to
  $G$ using the universal property of the group presentation, where the map on generators is given by taking the
  singleton list. To construct the group homomorphism from $G$, we use the universal property of the set quotient, where
  the map on the underlying set is given by mapping $\inl$ on the list. Using that the relation is a congruence, we show
  that this constitutes a group isomorphism.
\end{proof}

@@

The inversion count of an element is given by the number of smaller elements that appear after it in the permutation.

@@

\noindent We can show that the function $\immersion_{n}$ gives an equivalence between $\Lehmer[n]$ and $\im{\normf}$.
